\vspace{-1in}Identity signaling model progress

### 2020-03-11 reports/Progress.tex
finished preliminary minority experiments
beginning refactor with writing README documenting how to run experiments

@@

>>>>

\subsubsection{Fraction of minorities = 0.05}

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/covert_series_majority_005.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/covert_series_minority_005.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \caption{Mean timeseries of the evolution of covert signaling in the
    majority (a) and minority (b) populations.}
  \label{fig:regressions}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/majority_signalers_005.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/minority_signalers_005.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \caption{Proprtion of covert signalers for different parameter settings in the
    majority (a) and minority (b) populations.}
  \label{fig:regressions}
\end{figure}

\begin{figure}[H]
  \centering
    \includegraphics[width=0.6\textwidth]{Figures/covert_signalers_diff_005.pdf}
  \caption{Difference between proportion of covert signalers in the minority 
    and majority populations. When cost of disliking is high and homophily is 
    low, more minority agents are covert signalers than majority agents,
    proportionally. An increase in homophily enables minority agents to 
    find one another more easily, so overt signaling, which reaches more of
    the population, is advantageous.
  }
  \label{fig:}
\end{figure}

@@

\subsubsection{Fraction of minorities = 0.05}

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/churlish_series_majority_005.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/churlish_series_minority_005.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \caption{Mean timeseries of the evolution of churlish receiving in the
    majority (a) and minority (b) populations.}
  \label{fig:regressions}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/majority_receivers_005.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/minority_receivers_005.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \caption{Proprtion of churlish receivers for different parameter settings in the
    majority (a) and minority (b) populations.}
  \label{fig:regressions}
\end{figure}

\begin{figure}[H]
  \centering
    \includegraphics[width=0.6\textwidth]{Figures/churlish_receivers_diff_005.pdf}
  \caption{Difference between proportion of churlish receivers in the minority 
    and majority populations. Here the dependence is primarily on homophily.
    If homophily is too low, the minority population cannot interact often
    enough with their in-group, and so must adopt a non-churlish stance towards
    others in order to not suffer cost of disliking penalties. Once the minority
    can reliably find its in-group members (increasing homophily) the minority
    can afford to assume they dislike others, since by and large they dislike
    the majority.
  }
  \label{fig:}
\end{figure}
